BEE Paper

### 2024-04-07 paper.qmd
formatting

# Data 
```{r}

# Define the cars vector with 5 values
cars <- c(1, 3, 6, 4, 9)

# Graph the cars vector with all defaults
plot(cars)
```

>>>>

# Data 
```{r}
# Load the experiment data
experiment_data <-
    read.csv("data/experiment_data.csv")

# Rename the columns to more meaningful names
colnames(experiment_data)[which(names(experiment_data) == "Q5a")] <-
    "group1_bid"
colnames(experiment_data)[which(names(experiment_data) == "Q5b")] <-
    "group2_bid"
colnames(experiment_data)[which(names(experiment_data) == "Q6")] <-
    "lived_abroad"
colnames(experiment_data)[which(names(experiment_data) == "Q7")] <-
    "travel_frequency"
colnames(experiment_data)[which(names(experiment_data) == "Q8")] <-
    "expenditure"

# Convert the values of the bid columns to pounds
experiment_data$group1_bid_in_pounds <-
    experiment_data$group1_bid * 5
experiment_data$group2_bid_in_pounds <-
    experiment_data$group2_bid / 5

# Plot a boxplot for columns the bid columns
boxplot(
    experiment_data$group1_bid_in_pounds,
    experiment_data$group2_bid_in_pounds,
    main = "Boxplot of group 1 and group 2 bids (in Pounds)",
    names = c("Group 1", "Group 2"),
    xlab = "Variables",
    ylab = "Values"
)
```
